Tensor anisotropy as a tracer of cosmic voids

### 2015-06-16 RefereeResponse.md

      Response: 
      - Although lambda_1 is the defining property of voids when using the T-web/V-web (1st paragraph of 
	subsec 3.2), the FA exihibit a key advantage that makes it a better void tracer (please refer to 
	3rd paragraph of subsec. 3.2 of the new version).
      - Now it is explicitly explained why the FA, as defined in the context of MRI, is useful to cosmologist 
	(6th paragraph of introduction and 1st paragraph of subsec 3.1).
      - A new figure (Fig 3.) was prepared. Histograms of the volume contribution of each environment for 
	each value of the FA (3rd paragraph of subsec. 3.2). Sheets (mainly) and filaments are clearly 
	associated with high values of the FA.

2. **I did not understand the sentence at the end of Sect 2, "In this work we propose an optimal value of 
    the threshold based on the maximization of the fractional anisotropy field in the locations label[ed] 
    as filaments and walls," and this seems to be an important point. Is the threshold mentioned in this 
    sentence a threshold in lambda_1, or FA? Is this the 0.95 threshold in FA? It seems to be a reasonable 
    choice, but I do not see a sense in which it is "optimal," except that it seems to be the boundary 
    between the FA being well-correlated with lambda_1 and not-so-well. Also, if this sentence is about the 
    0.95 threshold, I do not see why it "does not enter into our computations," since the boundary of many 
    voids will depend on this threshold. It would be useful to know for what fraction of voids the limit 
    FA = 0.95 actually affects the boundary (in the case of the largest voids, I suppose).**

3. **I do not see how the value of FA=0.65 (corresponding to lambda_1 = 0) is used "to remove ridges."**

    Response: 
    - We have improved our explanation about the ridge removing
    procedure in the 3rd paragraph of subsection 3.3.

@@

4. **In Fig. 6, I only see a clear ridge in FA at r~r_eff in a few
    cases. the sentence in Sect. 5.5 "The  difference between the
    radius where the density ridge is reached ([r/]reff = 3) and the
    radius of the  FA ridge ([r/]reff = 1 ) ..." implies that I should
    see a ridge in FA at r~r_eff. Is this because the ridge is
    actually a 2D surface that is spherically averaged? It would be
    helpful to point this (or any  other reasons) out. Also, the
    statement "This makes the FA ridge a reasonable boundary for voids
    compared  to the traditional definition that puts the boundary at
    the density ridge" implies (perhaps  unintentionally) that the FA
    ridge is a superior marker of the edge of a void than a density
    ridge. It is  a physically different sort of ridge, and I agree
    that it is reasonable, but I do not see why it should  be
    superior.**

    Response:
    - We now talk about "maxima" instead of "ridge" in the TA
    profiles. We have also removed the references of the TA as a
    "superior" characterization.

### 2015-06-16 cosmic_voids.tex
issue #16 solved

\after{The watershed algorithm also needs a threshold value to reduce
spurious features and prevent void hierarchization.  
If the density field is used, a typical threshold is
$\delta = -0.8$ \citep{Platen07},  which means that, given two neighbour 
voids, if the mean value of the density across their common boundary is 
below that threshold, both voids are taken as just one void.
In our case we have to find a corresponding FA value
to define this threshold.}
%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

In Fig. \ref{fig:L1_correlations} we find the correlations of
the eigenvalue $\lambda_1$ with the matter overdensity (left panel) and
the FA (right panel).
We can use this information to find the equivalent FA threshold. 
From the left panel we see that an underdensity of $\delta=-0.8$ 
corresponds to $\lambda_1=0.0$, regardless of the web-finding
scheme.
From the second panel we have a very tight correlation of $\lambda_1$
with the FA, indicating that in turn $\lambda_1=0.0$ corresponds to a
FA=$0.65$ which is the value that we choose to remove ridges. 
The right column in Fig. \ref{fig:FA_field} shows all the individual
voids that have been identified using the watershed algorithm on the
FA field.

>>>>

\after{The watershed algorithm also needs a threshold value to reduce
spurious features and prevent void hierarchization.  
If the density field is used, a typical threshold is
$\delta = -0.8$ \citep{Platen07},  which means that, given two neighbouring 
voids, if the mean value of the density across their common boundary is 
below that threshold, the two voids are merged.
In our case we have to find a corresponding FA value
to define this threshold.}
%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

\after{In the left panel of Fig. \ref{fig:L1_correlations} we see how 
the FA correlates with the matter overdensity. 
A value of $\delta=-0.8$ corresponds to a value of $FA\sim 0.65$ regardless of
the web-finding scheme. 
This is the value we choose to remove ridges between two watershed
voids. 
The right column in Fig. \ref{fig:FA_field} shows all the individual
voids that have been identified using the watershed algorithm on the
FA field.}
